Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs

### 2015-11-26 papers/MbhMsph/mm.tex
sex

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, $M_{\rm BH}$, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between $M_{\rm BH}$ 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
While most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies,
our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
and define a tight 
\emph{red sequence} with intrinsic scatter $\epsilon_{(M_{\rm BH}|M_{\rm *,sph})} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
At the low-mass end, the bulges of late-type galaxies define a much steeper 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$ and $M_{\rm BH}/M_{\rm *,sph}$ equal to $0.02\%$ at $M_{\rm BH} \approx 10^6~\rm M_\odot$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) our S\'ersic galaxy sample follows $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, 
a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
-- once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

>>>>

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, $M_{BH}$, 
imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between $M_{BH}$ 
and the host spheroid (and galaxy) luminosity, $L_{sph}$ (and $L_{gal}$), 
and also stellar mass, $M_{*,sph}$.
While most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies,
our sample includes 17 spiral galaxies, half of which have $M_{BH}<10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{BH}~-~M_{*,sph}$ correlation.
The bulges of early-type galaxies follow $M_{BH}~\propto~M_{*,sph}^{1.04~\pm~0.10}$  
and define a tight 
\emph{red~sequence} with intrinsic scatter $\epsilon_{(M_{BH}|M_{*,sph})}~=~0.43~\pm~0.06\rm~dex$ 
and a median $M_{BH}/M_{*,sph}$ ratio of $0.68~\pm~0.04\%$, 
i.e.~a $\pm~2\sigma$ range of $0.1-5\%$.
At the low-mass end, the bulges of late-type galaxies define a much steeper 
\emph{blue~sequence}, 
with $M_{BH}~\propto~M_{*,sph}^{2-3}$ and $M_{BH}/M_{*,sph}$ equal to $0.02\%$ at $M_{BH}~\approx~10^6\rm~M_\odot$. 
%indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i)~our S\'ersic galaxy sample follows $M_{BH}~\propto~M_{*,sph}^{1.48~\pm~0.20}$, 
a less steep sequence than previously reported; 
ii)~bulges with S\'ersic index $n_{sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{BH}$ from the correlation defined by the current bulge sample with $n_{sph}>2$; 
and iii)~$L_{sph}$ and $L_{gal}$ correlate equally well with $M_{BH}$, in terms of intrinsic scatter, only for early-type 
galaxies~--~once reasonable numbers of spiral galaxies are included, the correlation with $L_{sph}$ is better than that with $L_{gal}$.

### 2015-11-26 papers/ellicular/ellicular.tex
sex

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

NGC 1277 \citep{vandenbosch2012,yildirim2015} and NGC 1332 \citep{rusli2011}.

@@

For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
In the unsharp mask, the green circles indicate the position of the two brighter spots associated to the edge-on nuclear ring. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

NGC 1277 \citep{vandenbosch2012,yildirim2015,walsh2015n1277} and NGC 1332 \citep{rusli2011}.

@@

For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{walsh2015n1277} 

@@

Note that for NGC 1277 we recover a spheroid stellar mass of $2.7 \times 10^{11}~\rm M_\odot$, 
in agreement with the value of $\approx 1-2 \times 10^{11}~\rm M_\odot$ obtained by \cite{emsellem2013} 
from his multi-Gaussian expansion models\footnote{In \cite{emsellem2013}, 
readers will find a clever discussion of the problematics asociated with the definition and the identification 
of the ``bulge'' component in a galaxy. }.  
